Hydra Battles in Coq

### 2020-11-05 doc/hydras.tex
corrections in documentation
correction of typos

@@

\begin{itemize}
\item Hercules chops off always the rightmost head of the hydra.
\item The battle is standard: at the round number $i$, the expected replication is $i$.
\end{itemize}

@@

We define an injection from the type \texttt{nat} into \texttt{Hydra}.
For any natural number $i$, $\iota(i)$ is the hydra composed of a foot and
$i+1$ heads at height $1$. For instance, Fig.~\ref{fig:flower} represents the hydra $\iota(3)$.

@@

Let us follow the same pattern as in Sect.~\ref{omega-case}.
First, we define an injection from type \texttt{t} into \texttt{Hydra}, by
 associating to  each ordinal $\omega\times i+ j = (i,j)$ the hydra with $i$ branches of length $2$ and
$j$ branches of length $1$.

@@

Then we have  three cases to consider, according to the values of $i$ and $j$.
\begin{itemize}
\item If $p=(0,0)$ then obviously, $\iota(p)\geq p = (0,0)$
\item If  $p=(i+1,0)$ for some $i\in\mathbb{N}$, we
 remark  that $p$ is strictly greater than any pair $ (i, j)$, where $j$ 
is any natural number.

@@

\subsubsection{End of the Proof}

Since $<$ is a strict order (irreflexive  and transitive) on \texttt{nat*nat}, we infer that there is no
variant for termination on the lexicographic square of $(\mathbb{N},<)$.

\begin{enumerate}
\item From \texttt{m\_lt}, we infer the strict inequality 
\texttt{m small\_h o< m big\_h}
\item from \texttt{m\_ge}, we get \texttt{m big\_h o<= m (iota (m big\_h)) = m small\_h} 
\end{enumerate}

\begin{Coqsrc}
Theorem Impossible : False.
Proof.
  destruct (StrictOrder_Irreflexive  (m big_h)).
  apply le2_lt2_trans with (m small_h).
  -  unfold small_h;  apply m_ge.
  -  apply m_lt. 
Qed.

@@

\item just go into the \texttt{theories} directory, and type "\texttt{make}"
\end{itemize}

>>>>

\item Just go into the root directory, and type "\texttt{make}"
\end{itemize}

@@

\begin{itemize}
\item At each round, Hercules chops off the rightmost head of the hydra.
\item The battle is standard: at the round number $i$, the expected replication is $i$.
\end{itemize}

@@

We define an injection $\iota$ from the type \texttt{nat} into \texttt{Hydra}.
For any natural number $i$, $\iota(i)$ is the hydra composed of a foot and
$i+1$ heads at height $1$. For instance, Fig.~\ref{fig:flower} represents the hydra $\iota(3)$.

@@

Let us follow the same pattern as in Sect.~\ref{omega-case}.
First, we define an injection $\iota$ from type \texttt{t} into \texttt{Hydra}, by
 associating to  each ordinal $\omega\times i+ j = (i,j)$ the hydra with $i$ branches of length $2$ and
$j$ branches of length $1$.

@@

Then we have  three cases to consider, according to the value of $p$.
\begin{itemize}
\item If $p=(0,0)$ then obviously, $\iota(p)\geq p = (0,0)$
\item If  $p=(i+1,0)$ for some $i\in\mathbb{N}$, we
 remark  that $p$ is strictly greater than any pair $ (i, j)$, where $j$ 
is any natural number.

@@

\subsubsection{End of the Proof}
From \texttt{m\_ge}, we get \texttt{m big\_h o<= m small\_h = m (iota (m big\_h)) }. 
Since $<$ is a strict order (irreflexive  and transitive), this inequality is incompatible with the strict inequality  \texttt{m small\_h o< m big\_h} (lemma \texttt{m\_lt}).

\vspace{4pt}
\noindent
In \coq (Module~\href{../theories/html/hydras.Hydra.Omega2_Small.html\#Impossible}{Hydra.Omega2\_Small}):

\begin{Coqsrc}
Theorem Impossible: False.
Proof.
  destruct (StrictOrder_Irreflexive (m big_h)).
  apply le2_lt2_trans with (m small_h).
  -  unfold small_h; apply m_ge.
  -  apply m_lt. 
Qed. 
End Impossibility_Proof.
\end{Coqsrc}

@@
